The effect of genetic linkage on island endemics richness

### 2018-08-20 paper/draft.tex
disc: reasons for temp dyns of radiations FL vs NL

\section{Discussion}
The fact that low-linkage (single) species speciated in general faster than their high-linkage counterparts
is in line with expectations given their higher potential for fast evolutionary response [as exemplified REFS].
What did come as a surprise, however was that, over time, high linkage lineages surpassed low linkage lineages
in the number of emerging species.

>>>>

\section{Discussion}
The fact that low-linkage (single) species speciated in general faster than their high-linkage counterparts
is in line with expectations given their higher potential for fast evolutionary response [as exemplified REFS].
What did come as a surprise, however was that, over time, high linkage lineages surpassed low linkage lineages
in the number of emerging species.
The reason for this is likely to be found in the high genetic variation throughout the high-linkage populations
due to genetic hitchhiking.
Combined with random drift, this genetic variation has a high potential of producing numerous species over time [non-adaptive radiation].
[EXAMPLES]
On the other hand, independent recombination of genes in low-linkage populations explains their quick adaptive response
to the conditions in their respective environments.
Once adapted and having reached a high degree of specialization, however, the genetic architecture leads to strong selection against
new and mainly deleterious mutations.
[EXAMPLES]

[SPECULATION:] In mixed community scenarios this effect becomes less clear as inter-lineage competition and red-queen-dynamics
present complex challenges.
